First Attempt at a Comparison Matrix

### 2014-08-15 test-compare-codes.Rmd
Create sorted list of code similarity

@@

Let's write that file to disk for someone who know about the history of codes to make sense of it.

```{r}
write.csv(triangle, "out/comparison_of_all_codes.csv")
```

@@

>>>>

Let's write that comparison to disk for someone who know about the history of codes to make sense of it.

```{r}
write.csv(comparison_of_all_codes, "out/comparison_of_all_codes.csv")
```

@@

@@

For each code we can get a sorted list of the codes that it is most like.

```{r}
for(i in 1:ncol(comparison_of_all_codes)) {
  x <- comparison_of_all_codes[,i]
  title <- colnames(comparison_of_all_codes)[i]
  cat("\n\n", title, " is most like:\n", sep = "")
  cat("---------\n")
  y <- sort(x, decreasing = TRUE)
  for(j in 2:length(y)) {
    cat(names(y)[j], y[j], "\n", sep = " ") 
    }
}
```
